Tracking and predicting turn structure during language acquisition

### 2014-09-11 paper/CasillasFrank-Anticip.tex
minor notes

@@

\subsubsection{Relationship with prior work}

@@

@@

FILL ME IN

>>>>

SCAFFOLDING: 1. QUESTIONS 2. INFORMATION INTEGRATION

@@

\subsection{Relationship with prior work}

@@

KEITEL??? STIMULUS DIFFERENCES? NUMBER OF TRIALS?  BUT WE REALLY DON'T KNOW. GENERAL CONSISTENCY - PROSODY DOES MATTER.

END BY HIGHLIGHTING OUR CONTRIBUTION - ISOLATE LEXICOSYNTAX

@@

Because early conversation plays a central role in children's language learning, we can not fully understand language acquisition without taking conversational skill into account. Conversation is the driving force behind what children say and hear, and participants have to know the rules of the game to play effectively---especially when multiple players are involved. Prediction allows ready speakers to get a word in at just the right moment. It also helps participants to comprehend  ongoing speech and catch onto potential misunderstandings via comparison to anticipated speech (e.g., `yes' or `no' in response to a polar question). Language is enormously helpful in making predictions of this type, and several studies have shown that adults rely on lexicosyntactic \citep{de-ruiter2006, magyari2012} and, to some extent, prosodic information \citep{ford1996, bogelsUndRev} in their turn-taking. FINISH IT!
% In the current study, we have tried to tie together several loose ends concerning when and how children begin to use linguistic information in their predictions about upcoming turn structure.
